---
title: "SpiderProject"
author: "Job Knoester"
date: "21 avril 2017"
output: html_document
---

# First analyses

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(include = TRUE)


tab <- read.csv2("~/etudes/Cours Master/Cours M2/Stage/SpiderProject/MeasureSpider.csv")
tab <- subset(tab, tab$Method == "Winkler48h")
tab <- tab[order(tab$Specimen),]


std <- read.delim2("~/etudes/Cours Master/Cours M2/Stage/SpiderProject/Standard.txt")

library(corrplot)
library(ggplot2)
library(plotly)
library(GGally)
library(ade4)
library(mice)
library(reshape2)
library(FD)
library(gridExtra)
library(explor)
library(picante)
library(parallel)
library(hypervolume)
library(moments)
library(cati)


```

## Manipulation step of the dataset

- Unused column and line already eliminated in the CSV 
- Graduation modified in milimeters
- Spider smaller than 0.4025mm eliminated
- NAs completed with the **mice package**
- Traits weighting
- Data + 1
- Log-transphormation
- Center/scale
- PCA 4 axes
- FD calculing

## Strategic dataset controle point

- Taxa subseting (salticidae, blind spider, ...)
- Weiting metodology
- Log tranformation
- PCA axes or traits
- Number of axes
- Number of traits (eliminate palp, replace male palp with **mice** data, fusioning fang and chel)
- Analyse traits one by one
- Measure convex hull volume or hyper volume
- Use package FD or not
- Creat guild by clustering

## Loading data, transphorme graduations into milimetres, complete NAs

All data about spider is in MeasureSpider.csv

The function *transformation* is used to convert the ocular graduation measure in milimeters. It use the zoom level column, the coresponding measure columns and the **standard** table. This new data is save in **measure** table. The **completmeasure** table contain only the spiders with a cephalotorax >= 0.4025 mm (or 2.5 graduation in zoom 6). Then, the NA is replaced by logical value with the package **mice**.


```{r, include=FALSE}
transformation <- function (colzoom1, coltransform1, colzoom2, coltransform2, colzoom3, coltransform3, data) 
{cbind(data[-c(colzoom1, coltransform1, colzoom2, coltransform2, colzoom3, coltransform3)],
      data[,coltransform1]*std$standard[match(data[,colzoom1],std$zoom)],
      data[,coltransform2]*std$standard[match(data[,colzoom2],std$zoom)],
      data[,coltransform3]*std$standard[match(data[,colzoom3],std$zoom)])
  }

measure <- transformation(colzoom1 = 5, coltransform1 = c(6:9), 
                      colzoom2 = 10, coltransform2 = c(11:12), 
                      colzoom3 = 13, coltransform3 = c(14:18),
                      data = tab)

measure <- measure[which(is.na(measure$LengthCephalo)==FALSE),]
measure <- subset(measure, measure$LengthCephalo >= 0.4025)

completmeasuremean <- mice(measure[,10:20], seed = 1)
completmeasure <- complete(completmeasuremean, 1)
completmeasure <- cbind(measure[,c(1:9)],completmeasure)

```

In the **proportion** table, all the morphometrics measure from the **completmeasure** table is weighted. (The body size is given by the give the body area ($Lceph*Wceph+Labdo*Wabdo$). The weighted leg size is given by the mean of femur 1 and 3 divided by the cephalotorax length. The larger eye size is weighted by the cephalotoxax width. Chelicera area is divided by the chephalotorax area. The paplus tarse length is weighted by the cephalotoxax length.

```{r}
proportion <- cbind(completmeasure[,c(1:9)],
                    completmeasure$LengthCephalo*completmeasure$WidthCephalo+completmeasure$LengthAbdomen*completmeasure$WidthAbdomen,
                    ((completmeasure$LengthF1femur+completmeasure$LengthF3femur)/2)/completmeasure$LengthCephalo,
                    completmeasure$LengthEye/completmeasure$WidthCephalo,
                    (completmeasure$LengthChelicera*completmeasure$WidthChelicera)/(completmeasure$LengthCephalo*completmeasure$WidthCephalo),
                    completmeasure$LengthFang/completmeasure$WidthChelicera,
                    completmeasure$LengthPalpusTarsus/completmeasure$LengthCephalo
                    )

names(proportion)[c(10:15)] <- c("body","leg","eye","chel","fang","palp")

```

Here particular taxa is remooved
```{r}
# proportion <- subset(proportion, proportion$Taxo != "blond white salticidae")
# proportion <- subset(proportion, proportion$Taxo != "salticidae")
# proportion <- subset(proportion, proportion$Taxo != "white salticidae")
# proportion <- subset(proportion, proportion$Taxo != "whitesalticideae")
# proportion <- subset(proportion, proportion$eye != 0)
```

Transphoration of the proportion data.
```{r}
proportionlog <- cbind(proportion[,c(1:9)],log(proportion[,c(10:15)]+1))
proportionsqrt <- cbind(proportion[,c(1:9)],sqrt(proportion[,c(10:15)]))
```

## Correlation Plots

```{r, fig.height=10, fig.width=10}
# corrplot.mixed(cor(proportion[,c(10:15)], use = "pairwise.complete.obs"))
#ggpairs(proportion, mapping = aes(color = Transect, alpha = 0.3), columns = 10:15)
ggpairs(proportionlog, mapping = aes(color = Transect, alpha = 0.3), columns = 10:15)
#ggpairs(proportionsqrt, mapping = aes(color = Transect, alpha = 0.3), columns = 10:15)

```

## Traits distributions
### Palpus with stage and sex

```{r}
a <- ggplot(proportion, aes(y=palp, x=proportion$StageSex)) +
  geom_boxplot()
  
pairwise.wilcox.test(proportion$palp,proportion$StageSex)
```


other traits
```{r, fig.height=10, fig.width=10}
a1 <- ggplot(proportion[,c(6,7,10)], aes(x=body, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
b1 <- ggplot(proportion[,c(6,7,11)], aes(x=leg, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
c1 <- ggplot(proportion[,c(6,7,12)], aes(x=eye, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
d1 <- ggplot(proportion[,c(6,7,13)], aes(x=chel, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
e1 <- ggplot(proportion[,c(6,7,14)], aes(x=fang, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
f1 <- ggplot(proportion[,c(6,7,15)], aes(x=palp, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')

a2 <- ggplot(proportion[,c(6,10)], aes(x=body, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
b2 <- ggplot(proportion[,c(6,11)], aes(x=leg, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
c2 <- ggplot(proportion[,c(6,12)], aes(x=eye, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
d2 <- ggplot(proportion[,c(6,13)], aes(x=chel, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
e2 <- ggplot(proportion[,c(6,14)], aes(x=fang, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
f2 <- ggplot(proportion[,c(6,15)], aes(x=palp, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)

a3 <- ggplot(proportionlog[,c(6,7,10)], aes(x=body, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
b3 <- ggplot(proportionlog[,c(6,7,11)], aes(x=leg, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
c3 <- ggplot(proportionlog[,c(6,7,12)], aes(x=eye, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
d3 <- ggplot(proportionlog[,c(6,7,13)], aes(x=chel, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
e3 <- ggplot(proportionlog[,c(6,7,14)], aes(x=fang, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')
f3 <- ggplot(proportionlog[,c(6,7,15)], aes(x=palp, fill=Plot)) +  geom_density(aes(colour=Transect), alpha = 0, size=1) +
  theme(legend.position='none')

a4 <- ggplot(proportionlog[,c(6,10)], aes(x=body, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
b4 <- ggplot(proportionlog[,c(6,11)], aes(x=leg, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
c4 <- ggplot(proportionlog[,c(6,12)], aes(x=eye, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
d4 <- ggplot(proportionlog[,c(6,13)], aes(x=chel, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
e4 <- ggplot(proportionlog[,c(6,14)], aes(x=fang, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)
f4 <- ggplot(proportionlog[,c(6,15)], aes(x=palp, fill=Transect)) +  geom_density(aes(colour=Transect), alpha = 0.3, size = 1)

grid.arrange(a1,a2,b1,b2,c1,c2,d1,d2,e1,e2,f1,f2, ncol=2)
grid.arrange(a3,a4,b3,b4,c3,c4,d3,d4,e3,e4,f3,f4, ncol=2)


#grid.arrange(a1,a2,a3,a4,b1,b2,b3,b4,c1,c2,c3,c4,d1,d2,d3,d4,e1,e2,e3,e4,f1,f2,f3,f4, ncol=2)# pairwise.wilcox.test(proportion$body,proportion$Transect)
# pairwise.wilcox.test(proportion$leg,proportion$Transect)
# pairwise.wilcox.test(proportion$eye,proportion$Transect)
# pairwise.wilcox.test(proportion$chel,proportion$Transect)
# pairwise.wilcox.test(proportion$fang,proportion$Transect)
# pairwise.wilcox.test(proportion$palp,proportion$Transect)

normalitytest <- matrix(nrow = 12,ncol = 6)
normalitytestlog <- matrix(nrow = 12,ncol = 6)
normalitytestsqrt <- matrix(nrow = 12,ncol = 6)
besttrans <- matrix(nrow = 12,ncol = 6)
colnames(normalitytest) <- colnames(proportion[,10:15])
colnames(normalitytestlog) <- colnames(proportion[,10:15])
colnames(normalitytestsqrt) <- colnames(proportion[,10:15])
colnames(besttrans) <- colnames(proportion[,10:15])
rownames(normalitytest) <- c(names(summary(proportion$Plot)),names(summary(proportion$Transect)))
rownames(normalitytestlog) <- c(names(summary(proportion$Plot)),names(summary(proportion$Transect)))
rownames(normalitytestsqrt) <- c(names(summary(proportion$Plot)),names(summary(proportion$Transect)))
rownames(besttrans) <- c(names(summary(proportion$Plot)),names(summary(proportion$Transect)))

for (i in 1:9) {
  for (j in 1:3) {
    for (k in 1:6) {
      normalitytest[i,k] <- shapiro.test(subset(proportion[,k+9],proportion$Plot==names(summary(proportion$Plot))[i]))$p
      normalitytestlog[i,k] <- shapiro.test(subset(proportionlog[,k+9],proportionlog$Plot==names(summary(proportionlog$Plot))[i]))$p
      normalitytestsqrt[i,k] <- shapiro.test(subset(proportionsqrt[,k+9],proportionsqrt$Plot==names(summary(proportionsqrt$Plot))[i]))$p
      
      normalitytest[j+9,k] <- shapiro.test(subset(proportion[,k+9],proportion$Transect==names(summary(proportion$Transect))[j]))$p
      normalitytestlog[j+9,k] <- shapiro.test(subset(proportionlog[,k+9],proportionlog$Transect==names(summary(proportionlog$Transect))[j]))$p
      normalitytestsqrt[j+9,k] <- shapiro.test(subset(proportionsqrt[,k+9],proportionsqrt$Transect==names(summary(proportionsqrt$Transect))[j]))$p
      
      if (which.max(c(normalitytest[i,k],normalitytestlog[i,k],normalitytestsqrt[i,k])) == 1) {
        besttrans[i,k] <- paste("none",":", round(normalitytest[i,k],4)*100,"%")}
      if (which.max(c(normalitytest[i,k],normalitytestlog[i,k],normalitytestsqrt[i,k])) == 2) {
        besttrans[i,k] <- paste("log",":", round(normalitytestlog[i,k],4)*100,"%")}
      if (which.max(c(normalitytest[i,k],normalitytestlog[i,k],normalitytestsqrt[i,k])) == 3) {
        besttrans[i,k] <- paste("sqrt",":", round(normalitytestsqrt[i,k],4)*100,"%")}
            
      if (which.max(c(normalitytest[j+9,k],normalitytestlog[j+9,k],normalitytestsqrt[j+9,k])) == 1) {
        besttrans[j+9,k] <- paste("none",":", round(normalitytest[j+9,k],4)*100,"%")}
      if (which.max(c(normalitytest[j+9,k],normalitytestlog[j+9,k],normalitytestsqrt[j+9,k])) == 2) {
        besttrans[j+9,k] <- paste("log",":", round(normalitytestlog[j+9,k],4)*100,"%")}
      if (which.max(c(normalitytest[j+9,k],normalitytestlog[j+9,k],normalitytestsqrt[j+9,k])) == 3) {
        besttrans[j+9,k] <- paste("sqrt",":", round(normalitytestsqrt[j+9,k],4)*100,"%")}
    }
  }
}

normalitytest
normalitytestlog
normalitytestsqrt
besttrans


```
# Traits suding :

```{r, fig.height=8, fig.width=12}
basematrix <- matrix(nrow = 9,ncol = 6)
colnames(basematrix) <- colnames(proportionlog[,10:15])
rownames(basematrix) <- names(summary(proportionlog$Plot))
basematrix <- as.data.frame(basematrix)

cwm <- basematrix
cwr <- basematrix
cwv <- basematrix
cws <- basematrix
cwk <- basematrix

for (i in 1:9) {   for (k in 1:6) {
  cwm[i,k] <- mean(subset(proportionlog[,k+9],proportionlog$Plot==names(summary(proportionlog$Plot))[i]))
  cwv[i,k] <- var(subset(proportionlog[,k+9],proportionlog$Plot==names(summary(proportionlog$Plot))[i]))
  cwr[i,k] <- max(subset(proportionlog[,k+9],proportionlog$Plot==names(summary(proportionlog$Plot))[i]))-min(subset(proportionlog[,k+9],proportionlog$Plot==names(summary(proportionlog$Plot))[i]))
  cws[i,k] <- skewness(subset(proportionlog[,k+9],proportionlog$Plot==names(summary(proportionlog$Plot))[i]))
  cwk[i,k] <- kurtosis(subset(proportionlog[,k+9],proportionlog$Plot==names(summary(proportionlog$Plot))[i]))
}}

colnames(cwm) <- paste("cwm",colnames(cwm),sep="")
colnames(cwr) <- paste("cwr",colnames(cwr),sep="")
colnames(cwv) <- paste("cwv",colnames(cwv),sep="")
colnames(cws) <- paste("cws",colnames(cws),sep="")
colnames(cwk) <- paste("cwk",colnames(cwk),sep="")
transect <- c("800m","800m","800m","600m","600m","600m","450m","450m","450m")
plot <- names(summary(proportionlog$Plot))
traitsdata <- cbind(transect,plot,cwm,cwr,cwv,cws,cwk)

cwm1 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwmbody, color=transect), size = 3) + theme(legend.position='none')
cwm2 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwmleg, color=transect), size = 3) + theme(legend.position='none')
cwm3 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwmeye, color=transect), size = 3) + theme(legend.position='none')
cwm4 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwmchel, color=transect), size = 3) + theme(legend.position='none')
cwm5 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwmfang, color=transect), size = 3) + theme(legend.position='none')
cwm6 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwmpalp, color=transect), size = 3) + theme(legend.position='none')

cwv1 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwvbody, color=transect), size = 3) + theme(legend.position='none')
cwv2 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwvleg, color=transect), size = 3) + theme(legend.position='none')
cwv3 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwveye, color=transect), size = 3) + theme(legend.position='none')
cwv4 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwvchel, color=transect), size = 3) + theme(legend.position='none')
cwv5 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwvfang, color=transect), size = 3) + theme(legend.position='none')
cwv6 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwvpalp, color=transect), size = 3) + theme(legend.position='none')

cwr1 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwrbody, color=transect), size = 3) + theme(legend.position='none')
cwr2 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwrleg, color=transect), size = 3) + theme(legend.position='none')
cwr3 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwreye, color=transect), size = 3) + theme(legend.position='none')
cwr4 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwrchel, color=transect), size = 3) + theme(legend.position='none')
cwr5 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwrfang, color=transect), size = 3) + theme(legend.position='none')
cwr6 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwrpalp, color=transect), size = 3) + theme(legend.position='none')

cws1 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwsbody, color=transect), size = 3) + theme(legend.position='none')
cws2 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwsleg, color=transect), size = 3) + theme(legend.position='none')
cws3 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwseye, color=transect), size = 3) + theme(legend.position='none')
cws4 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwschel, color=transect), size = 3) + theme(legend.position='none')
cws5 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwsfang, color=transect), size = 3) + theme(legend.position='none')
cws6 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwspalp, color=transect), size = 3) + theme(legend.position='none')

cwk1 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwkbody, color=transect), size = 3) + theme(legend.position='none')
cwk2 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwkleg, color=transect), size = 3) + theme(legend.position='none')
cwk3 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwkeye, color=transect), size = 3) + theme(legend.position='none')
cwk4 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwkchel, color=transect), size = 3) + theme(legend.position='none')
cwk5 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwkfang, color=transect), size = 3) + theme(legend.position='none')
cwk6 <- ggplot(traitsdata) + geom_point(aes(x=transect, y=cwkpalp, color=transect), size = 3) + theme(legend.position='none')



grid.arrange(cwm1,cwm2,cwm3,cwm4,cwm5,cwm6,cwv1,cwv2,cwv3,cwv4,cwv5,cwv6,cwr1,cwr2,cwr3,cwr4,cwr5,cwr6,cws1,cws2,cws3,cws4,cws5,cws6,cwk1,cwk2,cwk3,cwk4,cwk5,cwk6, ncol=6)
```
# Nul model generation

```{r}
nrep <- 1:9999

basematrix <- matrix(nrow = 9,ncol = 6)
colnames(basematrix) <- colnames(proportionlog[,10:15])
rownames(basematrix) <- names(summary(proportionlog$Plot))
basematrix <- as.data.frame(basematrix)
traitssamp <- list()

for (j in nrep) {
  cwm <- basematrix
  cwr <- basematrix
  cwv <- basematrix
  cws <- basematrix
  cwk <- basematrix
  proportionsamp <- proportionlog
  
  set.seed(j)
  
  proportionsamp$Plot <- sample(proportionsamp$Plot, length(proportionsamp$Plot), replace = F)
  
  for (i in 1:9) {   
    for (k in 1:6) {
      cwm[i,k] <- mean(subset(proportionsamp[,k+9],proportionsamp$Plot==names(summary(proportionsamp$Plot))[i]))
      cwv[i,k] <- var(subset(proportionsamp[,k+9],proportionsamp$Plot==names(summary(proportionsamp$Plot))[i]))
      cwr[i,k] <- max(subset(proportionsamp[,k+9],proportionsamp$Plot==names(summary(proportionsamp$Plot))[i]))-min(subset(proportionsamp[,k+9],proportionsamp$Plot==names(summary(proportionsamp$Plot))[i]))
      cws[i,k] <- skewness(subset(proportionsamp[,k+9],proportionsamp$Plot==names(summary(proportionsamp$Plot))[i]))
      cwk[i,k] <- kurtosis(subset(proportionsamp[,k+9],proportionsamp$Plot==names(summary(proportionsamp$Plot))[i]))
    }
  }
  
  colnames(cwm) <- paste("cwm",colnames(cwm),sep="")
  colnames(cwv) <- paste("cwv",colnames(cwv),sep="")
  colnames(cwr) <-paste("cwr",colnames(cwr),sep="")
  colnames(cws) <-paste("cws",colnames(cws),sep="")
  colnames(cwk) <-paste("cwk",colnames(cwk),sep="")
  
  transect <- c("800m","800m","800m","600m","600m","600m","450m","450m","450m")
  plot <- names(summary(proportionlog$Plot))
  
  traitssamp[[j]] <- cbind(transect,plot,cwm,cwr,cwv,cws,cwk)
}

traitssamp3d <- array(unlist(traitssamp), dim=c(dim(traitssamp[[1]]),length(traitssamp)),dimnames = list(rownames(traitssamp[[1]]), colnames(traitssamp[[1]]), nrep))
traitssamp3d <- aperm(traitssamp3d)

```


```{r}

nplot <- 1:9
nind <- 1:30

par(mfrow=c(6,5))
for (i in nplot) {   
  for (k in nind) {
        # pvalue <- (rank(c(traitsdata[i,k], traitssamp3d[,k,i]))/(nrep+1))[1]
    plot(density(traitssamp3d[,k,i]))#, main = paste('pvalue =', round(pvalue, 2)))
    abline(v = traitsdata[i,k+2], lwd = 2, col = 'red')
  }
}


pvalue <- matrix(nrow = 9,ncol = 32)
colnames(pvalue) <- colnames(traitsdata)
rownames(pvalue) <- rownames(traitsdata)
pvalue <- as.data.frame(pvalue)
pvalue[,1] <- transect 
pvalue[,2] <- plot

for (i in nplot) {   
  for (k in nind) {
    pvalue[i,k+2] <- (rank(unname(c(traitsdata[i,k+2], traitssamp3d[,k+2,i])))/(length(nrep)+1))[1]
    if (pvalue[i,k+2]<0.025) {pvalue[i,k+2] <- paste("SE",":",pvalue[i,k+2])}
    else{if (pvalue[i,k+2]>0.975) {pvalue[i,k+2] <- paste("HE",":",pvalue[i,k+2])}
    else {pvalue[i,k+2] <- paste("exp",":",pvalue[i,k+2])}}
  }
}

pvalue



a3 <- ggplot() +  geom_density(aes(x=as.matrix(traitssamp3d[,6,1])), alpha = 0, size=1) + 
  geom_vline(aes(xintercept=0), color="blue", size=0.5) +
  theme(legend.position='none')




```



# PCA

## PCA center scaled with log-transformed traits
```{r}
pcaproportionlog <- dudi.pca(proportionlog[,c(10:15)], center=T, scale=T, scannf = F, nf = 4)
# barplot((pcaproportionlog$eig/length(pcaproportionlog$eig))*100)
# pcaproportionlog$eig
# pcaproportionlog$co
```

## Diversity indices with transects as communities
```{r}
proportionlogmatrix <- proportionlog[,c(10:15)]
row.names(proportionlogmatrix) <- proportionlog[,2]

abundancematrixTransect <- dcast(proportionlog, Transect~Specimen, length)
row.names(abundancematrixTransect) <- abundancematrixTransect[,1]
abundancematrixTransect <- abundancematrixTransect[,2:dim(abundancematrixTransect)[2]] 

FDproportionlogTransect <- dbFD(x = proportionlogmatrix, a = abundancematrixTransect, w.abun = FALSE, stand.x = TRUE, ord = c("podani", "metric"), asym.bin = NULL, calc.FRic = TRUE, m = 6, stand.FRic = FALSE, scale.RaoQ = FALSE, calc.FGR = FALSE, clust.type = "ward", km.inf.gr = 2, km.sup.gr = nrow(x) - 1, km.iter = 100, km.crit = c("calinski", "ssi"), calc.CWM = TRUE, CWM.type = c("dom", "all"), calc.FDiv = TRUE, dist.bin = 2, print.pco = FALSE, messages = TRUE)

FDTransect <- as.data.frame(cbind(FDproportionlogTransect$FRic,FDproportionlogTransect$FEve,FDproportionlogTransect$FDiv,FDproportionlogTransect$FDis,FDproportionlogTransect$RaoQ))
colnames(FDTransect) <- c("FRic","FEve","FDiv","FDis","RaoQ")
Transect <- c("450m","600m","800m")
FDTransect <- cbind(Transect,FDTransect)
# FDTransect

```

## Diversity indices with plots as communities
```{r}
abundancematrixPlot <- dcast(proportionlog, Plot~Specimen, length)
row.names(abundancematrixPlot) <- abundancematrixPlot[,1]
abundancematrixPlot <- abundancematrixPlot[,2:dim(abundancematrixPlot)[2]] 

FDproportionlogPlot <- dbFD(x = proportionlogmatrix, a = abundancematrixPlot, w.abun = FALSE, stand.x = TRUE, ord = c("podani", "metric"), asym.bin = NULL, calc.FRic = TRUE, m = 6, stand.FRic = FALSE, scale.RaoQ = FALSE, calc.FGR = FALSE, clust.type = "ward", km.inf.gr = 2, km.sup.gr = nrow(x) - 1, km.iter = 100, km.crit = c("calinski", "ssi"), calc.CWM = TRUE, CWM.type = c("dom", "all"), calc.FDiv = TRUE, dist.bin = 2, print.pco = FALSE, messages = TRUE)

FDPlot <- as.data.frame(cbind(FDproportionlogPlot$FRic,FDproportionlogPlot$FEve,FDproportionlogPlot$FDiv,FDproportionlogPlot$FDis,FDproportionlogPlot$RaoQ))
colnames(FDPlot) <- c("FRic","FEve","FDiv","FDis","RaoQ")
Transect <- c("800m","800m","800m","600m","600m","600m","450m","450m","450m")
# Transect <- c(800,800,800,600,600,600,450,450,450)
FDPlot <- cbind(Transect,FDPlot)
# FDPlot
```

ploting results
```{r}
g <-  ggplot() + 
  geom_boxplot(data = FDPlot, aes(x=Transect, y=FRic),  colour="black") + 
  geom_point(data = FDTransect, aes(x= Transect, y = FRic), size = 3, colour = "red")
h <-  ggplot() + 
  geom_boxplot(data = FDPlot, aes(x=Transect, y=FEve),  colour="black") + 
  geom_point(data = FDTransect, aes(x= Transect, y = FEve), size = 3, colour = "red")
i <-  ggplot() + 
  geom_boxplot(data = FDPlot, aes(x=Transect, y=FDiv),  colour="black") + 
  geom_point(data = FDTransect, aes(x= Transect, y = FDiv), size = 3, colour = "red")
j <-  ggplot() + 
  geom_boxplot(data = FDPlot, aes(x=Transect, y=FDis),  colour="black") + 
  geom_point(data = FDTransect, aes(x= Transect, y = FDis), size = 3, colour = "red")
k <-  ggplot() + 
  geom_boxplot(data = FDPlot, aes(x=Transect, y=RaoQ),  colour="black") + 
  geom_point(data = FDTransect, aes(x= Transect, y = RaoQ), size = 3, colour = "red")

grid.arrange(g,h,i,j,k, ncol=2)

# pairwise.wilcox.test(FDPlot$FRic,FDPlot$Transect)
# pairwise.wilcox.test(FDPlot$FEve,FDPlot$Transect)
# pairwise.wilcox.test(FDPlot$FDiv,FDPlot$Transect)
# pairwise.wilcox.test(FDPlot$FDis,FDPlot$Transect)
# pairwise.wilcox.test(FDPlot$RaoQ,FDPlot$Transect)
# 
# cor.test(FDPlot$FRic,FDPlot$Transect, method = "spearman")
# cor.test(FDPlot$FEve,FDPlot$Transect, method = "spearman")
# cor.test(FDPlot$FDiv,FDPlot$Transect, method = "spearman")
# cor.test(FDPlot$FDis,FDPlot$Transect, method = "spearman")
# cor.test(FDPlot$RaoQ,FDPlot$Transect, method = "spearman")

```

## Nul model

```{r}

# cassique=list(NULL)
# awara=list(NULL)
# for(i in 1:49){ 
#   for(k in 1:49){
#     cassique[[k]] = randomizeMatrix(samp = abundancematrixPlot, null.model = "frequency", iterations = 50)
#   } 
#   awara[[i]] = dbFD(x = proportionlogmatrix, a = cassique[[i]], w.abun = TRUE, stand.x = TRUE, ord = c("podani", "metric"), asym.bin = NULL, corr = "lingoes", calc.FRic = TRUE, m = "min", stand.FRic = FALSE, scale.RaoQ = FALSE, calc.FGR=FALSE, calc.CWM = FALSE, CWM.type = c("dom", "all"), calc.FDiv = TRUE, dist.bin = 2, print.pco = FALSE, messages = FALSE)
# }
# 
# machoiron=as.data.frame(matrix(0,9,49)) 
# for(i in 1:49){ 
#   machoiron[,i]=data.frame(awara[[i]]$FRic)
# } 
# row.names(machoiron)=row.names(abundancematrixPlot)
# 
# machoiron <- t(machoiron)
# 
# z <- ggplot(machoiron, aes(x=machoiron[1,])) +
#   geom_density(alpha = 0.3, size = 1)
```

